The Folly of Password Policies: The case for organisations implementing technical alternatives over trying to manage users

### 2014-12-15 paper.tex
Severe cuts being made now.

One classical solution to weak passwords
has been to enforce password strength \emph{requirements}.
This is a technical solution whereby the systems simply
reject self-selected user passwords that do not conform
to a target strength or entropy.
This is a technical solution that shifts the burden forcibly onto
users and we can argue it is susceptible to the deliberate workarounds
that many users ultimately employ to reduce the overheads
in performing their primary jobs.

@@

There is certainly scope for further work to evaluate extensive
use of LinOTP and Kerberos within an enterprise setting as least as
a case study.

@@

Futher research may find a solution to storing keys
and certificates on a USB device without passwords or highlight
whether the risks of doing so are too high.

@@

The difficulty of eliminating a password or PIN from the login workflow
suggests that the PKI token or smartcard approach is more suitable for
situations where security requirements are higher and two-factor authentication
is preferable. The same technology is used for debit/credit card transactions
and for withdrawing cash from a bank account and thus we would expect it
to be used in other organisations that have similar security requirements.

@@

Given the wide variety of
options for integrating with services such as email, we did not go as far
as to evaluate them all and a thorough examination of a smartcard-based,
enterprise computer network is a subject for further research. The most
subtantial work in this area (that we know of) is from \textcite{grossesecuring}.
This research compares different smartcard technologies and software projects
and evaluates them for functionality that overlaps with the enterprise
requirements we are following in this paper. The information seems to be
quite dated now, 8 years later, as we have mentioned projects in this
section that cover functionality claimed not to exist -- especially for OpenPGP
cards.

@@

This also means all the benefits of OTP tokens as outlined in
section~\ref{sec:otp} apply also to the YubiKey. An additional benefit,
however, is that the YubiKey has a button on the device that types the
one-time password for the user, which allows not only for more secure tokens,
but also increases the overhead of the login process. The YubiKey achieves
this by acting as a USB keyboard during this operation.

@@

A drawback is that the YubiKey lacks additional storage for other certificates
or keys (as is the case with a USB storage device or an OpenPGP smartcard). This
makes it difficult to forward the authentication to remote systems. Yubico
produce the more expensive YubiKey Neo which supports OpenPGP and acts as
a smartcard. We did not evaluate this model in our test network.

Perhaps the most promising feature of the YubiKey for business use is the
ability to store a static password as well as the functionality above. A
managed distrubution of YubiKey hardward to employees within an organisation
could involve setting up each key with a strong, static password. The users
would not need to memorise the password, but it could be used as part of
a shared-credentials setup (e.g. LDAP directory service already established
within the organisation) without any significant changes to the technology
used.

In chapter~\ref{chapter:conclusion}, we explore the implication of the
static password feature within a company and draw some conclusions about the
different password alternatives and their use in the enterprise.

>>>>

Many companies enforce password strength \emph{requirements}.
This is a technical solution whereby the systems simply
reject self-selected user passwords that do not conform
to a target strength or entropy.
This shifts the burden forcibly onto
users and we can argue it is susceptible to the deliberate workarounds
that many users ultimately employ to reduce the overheads
in performing their primary jobs.

@@

@@

@@

@@

Given the wide variety of
options for smartcards, readers and supporting software, we were unable
to evaluate them all and a thorough examination of a smartcard-based,
enterprise computer network is a subject for further research. The most
subtantial work in this area (that we know of) is from \textcite{grossesecuring}.
This research compared different smartcard technologies and software projects
and evaluates them for functionality that overlaps with the enterprise
requirements we are following in this paper. The information seems to be
quite dated now, 8 years later, as we have mentioned projects in this
section that cover functionality claimed not to exist -- especially for OpenPGP
cards.

@@

This also means all the benefits of OTP tokens as outlined in
section~\ref{sec:otp} apply also to the YubiKey. An additional benefit,
however, is that the YubiKey has a button on the device that types the
one-time password for the user, which allows not only for more secure tokens,
but also increases the overhead of the login process.

@@

Perhaps the most promising feature of the YubiKey for business use is the
ability to store a static password as well as the functionality above. This
leads to the possibility of introducting the device in a way that is
compatible with exist applications that require a username and password.
